---
title: "bootstrapping_analysis"
author: "Marcell Püski"
date: '2022 szeptember 29 '
output: html_document
---


# import data sets 

These data tables were created by the bootstapping.Rmd script


```{r}

data_files <- list.files("../../data/bootstrapping")
data_list <- c()


for(i in 1:length(data_files)) {                              
  
  data_list[[i]] <-  assign(paste0("data_", i),                                   
         data.table(read.csv(paste0("../../data/bootstrapping/",
                   data_files[i]))))
}

```


# renaming variables

fix a data loading error in the variable names  

```{r}

for (i in 1:length(data_list)) {
  
  data_list[[i]] <- data_list[[i]] %>%
    rename(
    condition = 'ď.żfactor'
  )
}

```



# Best interventions

Here, I created a list of the serial numbers of the interventions with the highest scores in each sample.

```{r}
best_interventions <- c()

for (i in 1:length(data_list)) {
  
  best_interventions[i] <- data_list[[i]][1,2]
  
}

best_interventions <- unlist(best_interventions)

```


# best_interventions plot

```{r}
best_interventions_table <- data.table(table = c(1:length(best_interventions)), best_interventions = as.factor(best_interventions))

best_interventions_table <- best_interventions_table %>%
  group_by(best_interventions) %>%
  mutate(count_name_occurr = n())


ggplot(best_interventions_table, aes(x = reorder(best_interventions,-count_name_occurr), fill = factor(ifelse(best_interventions == 5, "first in the original study", "rest"))))+
  geom_bar(stat = "count")+
  scale_fill_manual(name = "", values = c("red", "grey50"), labels = c("most effective intervention in original study", "rest of the interventions")) +
  labs(title = "Most effective interventions\nper sample in bootstrapping analysis",
       x = "intervention serial number",
       y = "on how many samples they were most effective")+
  theme_ds4psy()


# How many times was the most effective intervention in the original study also the most effective in the bootstrapping analysis 
best_interventions_table %>%
  filter(best_interventions == 5) %>%
  count()

```


# create one dataset

```{r}

# provide numbering

for (i in 1:length(data_list)) {
  
  data_list[[i]] <- data_list[[i]] %>%
    mutate(dt_table = i)
}

# join them

all_results <- data_list[[1]]

for (i in 2:length(data_list)) {
  
  all_results <- full_join(all_results, data_list[[i]])
}


```



# create b values table

```{r}

b_values <- all_results %>%
  group_by(condition) %>%
  summarise(
    mean_b = mean(coef),
    standard_deviation = sd(coef),
    min = min(coef),
    max = max(coef)
  )

b_values <- b_values %>%
  arrange(desc(mean_b))

```



# distribution of the b value of intervention number five

```{r}
all_results %>%
  filter(treatment_number == 5) %>%
  ggplot(., aes(x = coef))+
  geom_histogram(binwidth = 0.1) +
  geom_vline(xintercept = 0.403, lwd = 1, colour = "red", linetype= "dotted")+
  geom_text(aes(x=0.403, label="\n         value measured in otiginal study", y=5), angle=90, text=element_text(size=11))+
  labs(title = "Distribution of the b value of the most \neffective intervention (number 5) in the bootstrapping analysis",
       x = "b value",
       y = "distribution")+
  theme_ds4psy()


```


# Combined best value in original study minus bootstrapping best results

```{r}
intervention_extra <- all_results %>%
  group_by(dt_table) %>%
  mutate(
    best_intervention_b = max(coef)
  ) %>%
  filter(treatment_number == 5)

b_kulonbseg <-  intervention_extra$best_intervention_b - intervention_extra$coef


sum(b_kulonbseg)

mean(b_kulonbseg)

```

# b values standard deviation averages

```{r}
mean(b_values$standard_deviation)

max(b_values$standard_deviation)

```

# b values tables

```{r}

b_ertekek <- b_values
b_ertekek$sorrend <- c(1:54)
b_ertekek <- b_ertekek %>%
  select(sorrend, condition, mean_b, standard_deviation, min, max)

b_ertekek$mean_b <- round(b_ertekek$mean_b, digits = 3)
b_ertekek$standard_deviation <- round(b_ertekek$standard_deviation, digits = 3)
b_ertekek$min <- round(b_ertekek$min, digits = 2)
b_ertekek$max <- round(b_ertekek$max, digits = 2)

kable(b_ertekek, col.names = c("sorrend", "Intervenció", "b érték átlaga", "b érték szórása", "minimum b érték", "maximum b érték"))

```

