---
title: "Sub group preparation"
author: "Marcell Püski"
date: '2022 szeptember 29 '
output: html_document
---


# libraries

```{r}
library(tidyverse)
library(data.table)
library(car)
library(survival)
library(lfe)
library(miceadds)

```


# load data

```{r}
metadata = data.table(read.csv("../../data/pptdata.csv"))

metadata[,intervention:=as.numeric(week %in% c(1:4))]

```


# data during intervention

```{r}
##-----Data during intervention-----:
metadata_during = metadata[week<=4 & week >= -52]
##Create weights:
#~~~T_i: length of panel of respective individual
#~~~Lc : length of respective cohort
#~~~Ngc: number of participants in respective group and cohort
metadata_during[,T_i:=.N, by = participant_id]
metadata_during[,time_weight:=as.numeric(Lc)/(T_i * Ngc)]
metadata_during = metadata_during[order(participant_id)]
metadata_during[,ind_weight:=1/T_i]
##Relevel factors so the Placebe Control is the reference group
metadata_during[,exp_condition:=as.factor(exp_condition)]
metadata_during[,exp_condition:=relevel(exp_condition, ref = "Placebo Control")]
metadata_during[,treatment_number:=as.numeric(exp_condition)]

```


# before intervention

```{r}
balance_pid_df <- readRDS("../../data/balance_pid_df.RDS") %>% 
  mutate(final_name = desc)

library(broom)

balance_pid_df$desc <- relevel(balance_pid_df$desc, ref = "Placebo Control")
balance_pid_df$cohort <- relevel(balance_pid_df$cohort, ref = "1234")

```


```{r}
weighted_gym_visits_final <- readRDS("../../data/weighted_gym_visits_final.RDS")

```


```{r}
pre_weeks_df <- weighted_gym_visits_final %>% 
  distinct(participant_id) %>% 
  mutate(weeks_count = 4) %>% 
  uncount(weeks_count, .id = "relative_weeks") %>% 
  mutate(relative_weeks = relative_weeks * -1) %>% 
  left_join(dplyr::select(weighted_gym_visits_final, participant_id, relative_weeks, week_visits), 
            by = c("participant_id", "relative_weeks")) %>% 
  mutate(week_visits = ifelse(is.na(week_visits), 0, week_visits)) %>% 
  group_by(participant_id) %>% 
  summarise(avg_four_week_visits = mean(week_visits)) %>% 
  left_join(distinct(balance_pid_df, participant_id, final_name), by = "participant_id")


avg_4_weeks_visit_df <- pre_weeks_df %>%
  select(participant_id, avg_four_week_visits)

```

# combine the two data set

```{r}
combined_dt <- metadata_during

combined_dt <- left_join(combined_dt, avg_4_weeks_visit_df)

```



# combined data function

```{r}
meta_regression_combined = function(period, weight, dv, robust = "none", ref = 'control'){
  ## period: either during, 4-week post-intervention or 10-week post-intervention
  ## weight: time-weighted (main one) or individual-weighted (robustness check #3)
  ## dv    : binary (whether visited the gym during a given week) or visits (weekly gym visits)
  ## robust: specify what robustness check to run (default to 'none' for main analysis)
  ## ref   : the reference treatment group, either "control" for Placebo Control or "mintreat" for Planning, Reminders and Micro-Incentives
  if(period == "during"){data = copy(combined_dt)} 
  if(period == "4post"){data = copy(metadata_4post)}
  if(period == "10post"){data = copy(metadata_10post)}
  if(dv == "visits"){data[,dv:=visits]}; if(dv == "binary"){data[,dv:=any_visit]} # specify dv
  if(robust == "intended"){ 
    ## Robustness check #1: Using intended treatment instead of assigned treatment
    data[,intended_exp_condition:=as.character(intended_exp_condition)]
    data[,intended_exp_condition:=relevel(as.factor(intended_exp_condition), ref = "Placebo Control")]
    data[,exp_condition:=intended_exp_condition]
    data[,treatment_number:=as.numeric(intended_exp_condition)]
    data[,Ngc_intended:=uniqueN(participant_id), list(exp_condition, cohort)]
    data[,time_weight:=as.numeric(Lc)/(Ngc_intended*T_i)]
  }
  if(robust == "collapse"){ 
    ## Robustness check #2: Without collapsing different versions of Planning, Reminders & Micro-incentives
    data[treatment == "1241C", exp_condition:="Planning, Reminders & Micro-Incentives to Exercise II"]
    data[treatment == "1253A", exp_condition:="Planning, Reminders & Micro-Incentives to Exercise III"]
    data[,treatment_number:=as.numeric(as.factor(exp_condition))]
    data[,Ngc_collapse:=uniqueN(participant_id), list(exp_condition, cohort)]
    data[,time_weight:=as.numeric(Lc)/(Ngc_collapse * T_i)]
  }
  if(weight == "time"){W = data$time_weight};  ## The main weighting scheme used throughout
  if(weight == "ind"){
    ## Robustness check #3: Obs weighted by individuals
    W = data$ind_weight
  }  
  if(period %in% c("4post", "10post") ){
    ## Post-intervention period data
    main_reg = felm(dv~factor(treatment_number)*intervention +
                      factor(treatment_number)*post_intervention|
                      factor(week):factor(cohort) + factor(participant_id)|0|
                      participant_id, data = data, weights = W,
                    exactDOF = TRUE)
    coeff     = coef(main_reg)
    main_coef = coeff[!is.nan(coeff)]
    
    coef_table = data.table(name = names(main_coef), est = main_coef)
    coef_table[,treatment_number:=gsub("factor(treatment_number)", "", name, fixed = TRUE)]
    coef_table[,treatment_number:=gsub(":post_intervention", "", treatment_number, fixed = TRUE)]
    coef_table[,treatment_number:=as.numeric(treatment_number)]
  }
  if(period == "during"){
    ## During intervention data
    main_reg = felm(dv~factor(treatment_number)*intervention|factor(week):factor(cohort) + factor(participant_id)|0|
                      participant_id, data = data, weights = W,
                    exactDOF = TRUE)
    coeff     = coef(main_reg)
    main_coef = coeff[!is.nan(coeff)]
    
    coef_table = data.table(name = names(main_coef), est = main_coef)
    coef_table[,treatment_number:=gsub("factor(treatment_number)", "", name, fixed = TRUE)]
    coef_table[,treatment_number:=gsub(":intervention", "", treatment_number, fixed = TRUE)]
    coef_table[,treatment_number:=as.numeric(treatment_number)]
  }
  ## Get clustered standard errors:
  HCmatrix = main_reg$clustervcv
  HCmatrix = HCmatrix[!is.na(coef(main_reg)),!is.na(coef(main_reg))]
    
  #----Wald tests---:
  ## This is to get pairwise Wald tests of coefficients to compare the experimental conditions
  H = rep(0, nrow(coef_table))
  G = length(unique(coef_table[!is.na(treatment_number)]$treatment_number))+1
  est_compare  = matrix(0, G, G)
  sd_compare   = matrix(0, G, G)
  pval_compare = matrix(0, G, G)
  ## some formatting below:
  for(t1 in 2:G){
    for(t2 in (1:(G-1))){
      H = rep(0, nrow(coef_table))
      H[coef_table[treatment_number==t1, which = TRUE]] = 1
      H[coef_table[treatment_number==t2, which = TRUE]] = -1
      est_compare[t1,t2]  = H %*% coef_table$est
      sd_compare[t1,t2]   = sqrt(c(HCmatrix %*% H) %*% H)
      pval_compare[t1,t2] =  linearHypothesis(main_reg, hypothesis.matrix = H, test = 'Chisq', vcov. = HCmatrix,
                                                singular.ok = TRUE)$`Pr(>Chisq)`[2]
    }
  }
  correct_est = function(X){
      X[,G]   = -X[G,]
      X[1,]   = -X[,1]
      diag(X) = 0
      return(X)
  }
  correct_err = function(X){
      X[,G]   = X[G,]
      X[1,]   = X[,1]
      diag(X) = 0
      return(X)
  }
    
  est_compare  = correct_est(est_compare)
  sd_compare   = correct_err(sd_compare)
  pval_compare = correct_err(pval_compare)
  #-----Create table of coefficients-----:
  treatment_code = data[,.(treatment_number = treatment_number[1]), 
                        factor(exp_condition)]
  treatment_code = treatment_code[order(treatment_number)]
  if(ref == "control"){ # If the reference group is "Placebo Control"
    treatment_code[,coef:=round(est_compare[,1], 3)]
    treatment_code[,sd:=round(sd_compare[,1], 3)]
    treatment_code[,pval:=round(pval_compare[,1], 3)]  
  }
    
    
  if(ref == 'mintreat'){# If the reference group is "Planning, Reminders, and Micro-Incentives"
    treatment_code[,coef:=round(est_compare[,44], 3)] 
    treatment_code[,sd:=round(sd_compare[,44], 3)]
    treatment_code[,pval:=round(pval_compare[,44], 3)]
    
  }
  ## %outperformed significantly:
  est_better   = est_compare  > 0
  pval_better5 = pval_compare < 0.05
  better5 = est_better * pval_better5
    
  ## Rsquared:
  a  = summary(main_reg)
  r2 = c(a$r.squared, a$adj.r.squared)
  return(list("model" = main_reg, 
                "r2"    = r2,
                "coef"  = treatment_code,
                "outperform" = better5,
                "pval_pairs" = pval_compare)) 
}


```



# analyses


## combined data
```{r}
main_2 = meta_regression_combined("during", "time", "visits") ## Main regression results
View(main_2$coef)                                    
setnames(main_2$coef, 'coef', 'coef_main')

```



## investigate variables

```{r}
#age
ggplot(combined_dt, aes(age)) +
  geom_histogram()

#before intervention gym
ggplot(combined_dt, aes(avg_four_week_visits)) +
  geom_histogram()


combined_dt %>%
  group_by(avg_four_week_visits) %>%
  count()

ggplot(combined_dt, aes(gender)) +
  geom_bar()

```



# Sub group analyses


## Create more flexible funkcion

```{r}
meta_regression_free = function(dt, period, weight, dv, robust = "none", ref = 'control'){
  ## period: either during, 4-week post-intervention or 10-week post-intervention
  ## weight: time-weighted (main one) or individual-weighted (robustness check #3)
  ## dv    : binary (whether visited the gym during a given week) or visits (weekly gym visits)
  ## robust: specify what robustness check to run (default to 'none' for main analysis)
  ## ref   : the reference treatment group, either "control" for Placebo Control or "mintreat" for Planning, Reminders and Micro-Incentives
  if(period == "during"){data = copy(dt)} 
  if(period == "4post"){data = copy(metadata_4post)}
  if(period == "10post"){data = copy(metadata_10post)}
  if(dv == "visits"){data[,dv:=visits]}; if(dv == "binary"){data[,dv:=any_visit]} # specify dv
  if(robust == "intended"){ 
    ## Robustness check #1: Using intended treatment instead of assigned treatment
    data[,intended_exp_condition:=as.character(intended_exp_condition)]
    data[,intended_exp_condition:=relevel(as.factor(intended_exp_condition), ref = "Placebo Control")]
    data[,exp_condition:=intended_exp_condition]
    data[,treatment_number:=as.numeric(intended_exp_condition)]
    data[,Ngc_intended:=uniqueN(participant_id), list(exp_condition, cohort)]
    data[,time_weight:=as.numeric(Lc)/(Ngc_intended*T_i)]
  }
  if(robust == "collapse"){ 
    ## Robustness check #2: Without collapsing different versions of Planning, Reminders & Micro-incentives
    data[treatment == "1241C", exp_condition:="Planning, Reminders & Micro-Incentives to Exercise II"]
    data[treatment == "1253A", exp_condition:="Planning, Reminders & Micro-Incentives to Exercise III"]
    data[,treatment_number:=as.numeric(as.factor(exp_condition))]
    data[,Ngc_collapse:=uniqueN(participant_id), list(exp_condition, cohort)]
    data[,time_weight:=as.numeric(Lc)/(Ngc_collapse * T_i)]
  }
  if(weight == "time"){W = data$time_weight};  ## The main weighting scheme used throughout
  if(weight == "ind"){
    ## Robustness check #3: Obs weighted by individuals
    W = data$ind_weight
  }  
  if(period %in% c("4post", "10post") ){
    ## Post-intervention period data
    main_reg = felm(dv~factor(treatment_number)*intervention +
                      factor(treatment_number)*post_intervention|
                      factor(week):factor(cohort) + factor(participant_id)|0|
                      participant_id, data = data, weights = W,
                    exactDOF = TRUE)
    coeff     = coef(main_reg)
    main_coef = coeff[!is.nan(coeff)]
    
    coef_table = data.table(name = names(main_coef), est = main_coef)
    coef_table[,treatment_number:=gsub("factor(treatment_number)", "", name, fixed = TRUE)]
    coef_table[,treatment_number:=gsub(":post_intervention", "", treatment_number, fixed = TRUE)]
    coef_table[,treatment_number:=as.numeric(treatment_number)]
  }
  if(period == "during"){
    ## During intervention data
    main_reg = felm(dv~factor(treatment_number)*intervention|factor(week):factor(cohort) + factor(participant_id)|0|
                      participant_id, data = data, weights = W,
                    exactDOF = TRUE)
    coeff     = coef(main_reg)
    main_coef = coeff[!is.nan(coeff)]
    
    coef_table = data.table(name = names(main_coef), est = main_coef)
    coef_table[,treatment_number:=gsub("factor(treatment_number)", "", name, fixed = TRUE)]
    coef_table[,treatment_number:=gsub(":intervention", "", treatment_number, fixed = TRUE)]
    coef_table[,treatment_number:=as.numeric(treatment_number)]
  }
  ## Get clustered standard errors:
  HCmatrix = main_reg$clustervcv
  HCmatrix = HCmatrix[!is.na(coef(main_reg)),!is.na(coef(main_reg))]
    
  #----Wald tests---:
  ## This is to get pairwise Wald tests of coefficients to compare the experimental conditions
  H = rep(0, nrow(coef_table))
  G = length(unique(coef_table[!is.na(treatment_number)]$treatment_number))+1
  est_compare  = matrix(0, G, G)
  sd_compare   = matrix(0, G, G)
  pval_compare = matrix(0, G, G)
  ## some formatting below:
  for(t1 in 2:G){
    for(t2 in (1:(G-1))){
      H = rep(0, nrow(coef_table))
      H[coef_table[treatment_number==t1, which = TRUE]] = 1
      H[coef_table[treatment_number==t2, which = TRUE]] = -1
      est_compare[t1,t2]  = H %*% coef_table$est
      sd_compare[t1,t2]   = sqrt(c(HCmatrix %*% H) %*% H)
      pval_compare[t1,t2] =  linearHypothesis(main_reg, hypothesis.matrix = H, test = 'Chisq', vcov. = HCmatrix,
                                                singular.ok = TRUE)$`Pr(>Chisq)`[2]
    }
  }
  correct_est = function(X){
      X[,G]   = -X[G,]
      X[1,]   = -X[,1]
      diag(X) = 0
      return(X)
  }
  correct_err = function(X){
      X[,G]   = X[G,]
      X[1,]   = X[,1]
      diag(X) = 0
      return(X)
  }
    
  est_compare  = correct_est(est_compare)
  sd_compare   = correct_err(sd_compare)
  pval_compare = correct_err(pval_compare)
  #-----Create table of coefficients-----:
  treatment_code = data[,.(treatment_number = treatment_number[1]), 
                        factor(exp_condition)]
  treatment_code = treatment_code[order(treatment_number)]
  if(ref == "control"){ # If the reference group is "Placebo Control"
    treatment_code[,coef:=round(est_compare[,1], 3)]
    treatment_code[,sd:=round(sd_compare[,1], 3)]
    treatment_code[,pval:=round(pval_compare[,1], 3)]  
  }
    
    
  if(ref == 'mintreat'){# If the reference group is "Planning, Reminders, and Micro-Incentives"
    treatment_code[,coef:=round(est_compare[,44], 3)] 
    treatment_code[,sd:=round(sd_compare[,44], 3)]
    treatment_code[,pval:=round(pval_compare[,44], 3)]
    
  }
  ## %outperformed significantly:
  est_better   = est_compare  > 0
  pval_better5 = pval_compare < 0.05
  better5 = est_better * pval_better5
    
  ## Rsquared:
  a  = summary(main_reg)
  r2 = c(a$r.squared, a$adj.r.squared)
  return(list("model" = main_reg, 
                "r2"    = r2,
                "coef"  = treatment_code,
                "outperform" = better5,
                "pval_pairs" = pval_compare)) 
}



```

## Gender

### Female

Female data set
```{r}
female_dt <- combined_dt %>%
  filter(gender == "F")

```

Female analyses
```{r}
main_female = meta_regression_free(female_dt, "during", "time", "visits") ## Main regression results
View(main_female$coef)                                    
setnames(main_female$coef, 'coef', 'coef_main')

results_female <- main_female$coef

```

### Male

male data set
```{r}
male_dt <- combined_dt %>%
  filter(gender == "M")

```


male analyses
```{r}
main_male = meta_regression_free(male_dt, "during", "time", "visits") ## Main regression results
View(main_male$coef)                                    
setnames(main_male$coef, 'coef', 'coef_main')

results_male <- main_male$coef

```


## Age

### Young (<=25)

young data set
```{r}
young_dt <- combined_dt %>%
  filter(age <= 25)

```

young analyses
```{r}
main_young = meta_regression_free(young_dt, "during", "time", "visits") ## Main regression results
View(main_young$coef)                                    
setnames(main_young$coef, 'coef', 'coef_main')

results_young <- main_young$coef

```

### Middle aged ( 25 < age <= 50)

middle_aged data set up
```{r}
middle_aged_dt <- combined_dt %>%
  filter(age > 25 & age <= 50)

```

middle_aged analyses
```{r}
main_middle_aged = meta_regression_free(middle_aged_dt, "during", "time", "visits") ## Main regression results
View(main_middle_aged$coef)                                    
setnames(main_middle_aged$coef, 'coef', 'coef_main')

results_middle_aged <- main_middle_aged$coef

```

### Old (>50)

```{r}
old_dt <- combined_dt %>%
  filter(age > 50)

```

old analyses
```{r}
main_old = meta_regression_free(old_dt, "during", "time", "visits") ## Main regression results
View(main_old$coef)                                    
setnames(main_old$coef, 'coef', 'coef_main')

results_old <- main_old$coef

```


## avarage gym visits before intervention

### not even once (0)

zero data set up
```{r}
zero_dt <- combined_dt %>%
  filter(avg_four_week_visits == 0)

```

zero analyses
```{r}
main_zero = meta_regression_free(zero_dt, "during", "time", "visits") ## Main regression results
View(main_zero$coef)                                    
setnames(main_zero$coef, 'coef', 'coef_main')

results_zero <- main_zero$coef

```


### few times (0 < gym visits <= 3)

few data set up
```{r}
few_dt <- combined_dt %>%
  filter(avg_four_week_visits > 0 & avg_four_week_visits <= 3)

```

few data analyses
```{r}
main_few = meta_regression_free(few_dt, "during", "time", "visits") ## Main regression results
View(main_few$coef)                                    
setnames(main_few$coef, 'coef', 'coef_main')

results_few <- main_few$coef

```


### often (3 < gym )

often data set up
```{r}
often_dt <- combined_dt %>%
  filter(avg_four_week_visits > 3)

```

often data analyses
```{r}
main_often = meta_regression_free(often_dt, "during", "time", "visits") ## Main regression results
View(main_often$coef)                                    
setnames(main_often$coef, 'coef', 'coef_main')

results_often <- main_often$coef

```


### almost daily (>5) --- (not used)

daily data set up
```{r}
daily_dt <- combined_dt %>%
  filter(avg_four_week_visits > 5)

```


daily data analyses
```{r}
main_daily = meta_regression_free(daily_dt, "during", "time", "visits") ## Main regression results
View(main_daily$coef)                                    
setnames(main_daily$coef, 'coef', 'coef_main')

results_daily <- main_daily$coef

```


## full - all of the data

```{r}
main_full = meta_regression_free(combined_dt, "during", "time", "visits") ## Main regression results
View(main_full$coef)                                    
setnames(main_full$coef, 'coef', 'coef_main')

results_full <- main_full$coef

```



# cheking number of participants in each condition

```{r}

often_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()


combined_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()

daily_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()

old_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()

middle_aged_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()

young_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()

few_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()

zero_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()

male_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()

female_dt %>%
  group_by(exp_condition) %>%
  distinct(participant_id) %>%
  count()

```


# exporting data sets

```{r}
write_excel_csv(combined_dt, path = ("../../data/combined_dt.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

```

# export results
```{r}
write_excel_csv(results_full, path = ("../../data/sub_group_data/result_full.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

write_excel_csv(results_daily, path = ("../../data/sub_group_data/results_daily.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

write_excel_csv(results_female, path = ("../../data/sub_group_data/results_female.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

write_excel_csv(results_few, path = ("../../data/sub_group_data/results_few.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

write_excel_csv(results_male, path = ("../../data/sub_group_data/results_male.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

write_excel_csv(results_middle_aged, path = ("../../data/sub_group_data/results_middle_aged.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

write_excel_csv(results_often, path = ("../../data/sub_group_data/results_often.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

write_excel_csv(results_old, path = ("../../data/sub_group_data/results_old.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

write_excel_csv(results_young, path = ("../../data/sub_group_data/results_young.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")

write_excel_csv(results_zero, path = ("../../data/sub_group_data/results_zero.csv"), na = "NA", append = FALSE,
  col_names = TRUE, delim = ",", quote_escape = "double")


```

