---
title: "Random forest analysis"
author: "Marcell Püski"
date: '2022 szeptember 29 '
output: html_document
---

# libraries

```{r}
library(tidyverse)
library(data.table)
library(caTools)
library(randomForest)
library(caret)
library(Metrics)
library(e1071)
library(ds4psy)

```


# load data

This data was created in the andom_forest_preparation.Rmd script

```{r}

df_simple <- data.table(read.csv("../../data/dt_simple.csv"))

```


# rename

```{r}
df_simple <- df_simple %>%
  rename(
    participant_id = 'ď.żparticipant_id'
  )


```


# using only relevant interventions


```{r}
df_best <- df_simple %>%
  filter(treatment_number == 5 | treatment_number == 21 | treatment_number == 40 | treatment_number == 53 | treatment_number == 2 | treatment_number == 3| treatment_number == 28 | treatment_number == 15 | treatment_number == 20 | treatment_number == 34 | treatment_number == 50 | treatment_number == 17 | treatment_number == 31)

df_best$treatment_number = as.factor(df_best$treatment_number)
df_best$exp_condition = as.factor(df_best$exp_condition)


```



# train set - test set
```{r}
set.seed(123)
split <- sample.split(df_best$participant_id, SplitRatio = 0.7)

train_df <- subset(df_best, split == "TRUE")
test_df <- subset(df_best, split == "FALSE")

```


# random forest
```{r}
set.seed(222)
rf_fit <- randomForest(intervention_effect ~ age+gender+treatment_number+before_avg, data = train_df, ntree = 500,
                       keep.forest=TRUE, importance=TRUE)


rf_fit

```



# performance on test set

```{r}
test_df$pred <- predict(rf_fit, newdata = test_df)

sqrt(sum((test_df$pred - test_df$intervention_effect)^2) / nrow(test_df))

```



# define best interventions/person 

## create data
```{r}
dt_predict <- df_best %>%
  select(participant_id, age, gender, before_avg, treatment_number)

```


# test
```{r}

alma <- dt_predict
alma$treatment_number <- as.factor(40)


alma$five_predict <- predict(rf_fit, alma)


```

# for loopos solution

```{r}
intervention_list <- c(5, 21, 40, 53, 2, 3, 28, 15, 20, 34, 50, 17, 31)

v <- list()

for (i in 1:length(intervention_list)) {
  
  a <- intervention_list[i]
  dt_predict$treatment_number <- as.factor(a)
  v[[i]] <- predict(rf_fit, dt_predict)
}

```


# put it in to one data table
```{r}
prediktalt_values <- data.table(
  ID =  dt_predict$participant_id,
  "5" =  v[[1]],
  "21" = v[[2]],
  "40" = v[[3]],
  "53" = v[[4]],
  "2" = v[[5]],
  "3" = v[[6]],
  "28" = v[[7]],
  "15" = v[[8]],
  "20" = v[[9]],
  "34" = v[[10]],
  "50" = v[[11]],
  "17" = v[[12]],
  "31" = v[[13]]
)


```

# long format

```{r}
prediktalt_values_long <- gather(data = prediktalt_values,
                            key = intervention,
                            value = prediction,
                            "5":"31")

```


# choosing best intervention

```{r}
prediktalt_values_long <- prediktalt_values_long %>%
  group_by(ID) %>%
  mutate(
    best_effect = max(prediction),
    best_intervention = case_when(best_effect == prediction ~ 1,
                                  best_effect != prediction ~ 0)
  )

best_intervention <- prediktalt_values_long %>%
  filter(best_intervention == 1)

```


# which interventioncio is best how many times
```{r}
best_intervention %>%
  group_by(intervention) %>%
  count()

```


# effect of intervention number 5

```{r}
intervention_5 <- prediktalt_values_long %>%
  filter(intervention == "5")

```


# best intervention minus intervention number 5

```{r}
# average intervention number 5 effect 
mean(intervention_5$prediction)
sd(intervention_5$prediction)

# average best intervention effect
mean(best_intervention$prediction)
sd(best_intervention$prediction)

# difference of the two
mean(best_intervention$prediction) - mean(intervention_5$prediction)


# What is the average percentage improvement in using the personally best intervention (predicted by the random forest model) compared to using only intervention number 5: 
(mean(best_intervention$prediction) - mean(intervention_5$prediction))/mean(intervention_5$prediction)*100


```

